Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Typos

The implementation we chose must also work after being compiled with the {\verb
-fPIC} flag in \ac{GCC}. This flag basically tells the compiler that the
machine code must be able to execute anywhere in memory, also known as position
independant. In runtime one extra \{CPU} register will be used for this. This
is needed because a Python C-module we will need to be compiled as a shred
library.

Since Tahoe-\ac{LAFS} is using \ac{SHA}-256 internally, we only test \ac{SHA}-3
functions with 256-bit output in our implementation.

@@

We chose the fastest implementation of each candidate that conforms to the
following criteria:
\paragraph{Criterion 1} The implementation must have an \ac{API} defined in C.
\paragraph{Criterion 2} The implementation must include a working {\verb update() } function.
\paragraph{Criterion 3} The implementation must not use assembly that can not be made
    position independent by \ac{GCC}.
\paragraph{Criterion 4} The implementation should conform to the \acp{KAT} specified in the
    \ac{NIST} submission package, or later updates by the author.

\vspace{12pt}
Based on these criteria, we choose the fastest possible implementation based on
our benchmark in \ac{SUPERCOP} \cite{s_tahoe_supercop}. The relative speed of
each implementation, in relation to other implementation for the same and other
candidates are available at source.

@@

The chosen implementations are shown in Table \ref{tbl:sha3:implementations}.
Their compiler flags used, which are extracted from the \ac{SUPERCOP} results,
can be seen in Table \ref{tbl:sha3:compilerflags}. Compiler flags are described
in the GCC manual\footnote{GCC Manual \url{http://gcc.gnu.org/onlinedocs/}},
and the one used for every implementation which might affect performance, are:

@@

\paragraph{JH} seems to be broken in every implementation with regard to
Criterion 2. For both the optimized versions found in \ac{SUPERCOP}, and the
reference implementations in the \ac{NIST} submission package,
{\verb Hash("foofoo") } will not yield the same result as two consecutive calls
to {\verb Update("foo") }. However, the implementation in sphlib does fulfill
this requirement. We have contacted the author, Thomas Pornin, which confirms
this problem with the official JH candidate, and that the author has been made
aware of the problem, but has not released any updated version yet
\cite{s_pornin}.

@@

Our original goal was to make SHA3lib include functionality to support all
output lengths, and not only 256-bit. This was based on our observation that the
official \ac{NIST} submission packages include ``all-in-one'' implementations
that support this. Later we observed that this is not the case for all
implementations in \ac{SUPERCOP}. Together with the fact that Tahoe-\ac{LAFS}
uses 256-bit output, in the end only included support for 256-bit output in
SHA3lib was implemented. The design we have used is shown in Figure
\ref{fig:python:inheritance}, and does follow the initial idea that SHA3lib
should support multiple output lengths.

@@

Basically the class \textbf{echo} resides in Cython and in C, and is responsible
for bringing the C functionality of the C implementation to Python. By compiling
\textbf{echo} it will be made available for use in Python.  The class
\textbf{echo256} is a simple Python class which inherits from \textbf{echo}. The
only action this class actually performs, is to set the output size to 256 bit. If
the underlying C-functions would have supported multiple output sizes, the same
could have been done to incorporate those.

@@

We then create a wrapper-class that mimics hashlib, this is shown in Listing
\ref{lst:cython_impl}. Functions declared with {\verb def } are Python
functions, {\verb cdef } are Cython-only functions, while {\verb cpdef } are
functions that can be accessed from both languages. While this is just the
implementation for the Echo candidate, the almost exact same pattern is used for
all of the other candidates.

@@

\subsection{Unit tests}
We Unit Test each new candidate implementation that is included SHA3lib, both
to verify our own work and to verify that the implementation from \ac{SUPERCOP}
actually are correct.

@@

All hashing operations requested by the Tahoe system is routed through a
couple of classes and functions, and the connection to the underlying hash
function library is made on only one line. This is displayed in Listing
\ref{lst:hashutil}.

@@

\section{Automatic testing and distribution}
We fully automate the testing procedure. This is achieved by the use of
software revision control systems, which distributes both the source code of
Tahoe-\ac{LAFS}, SHA3lib and shell-scripts for installation and configuration of
both. Configuration is mainly done by the use of regular expressions.

The outline of this procedure is:

@@

BLAKE, \ac{BMW}, and Luffa outperform \ac{SHA}-256 on cycles per
byte for all tests. For larger input sizes, Simd and Luffa also do the
calculations quicker than \ac{SHA}-256.

>>>>

The implementation we chose must also work after being compiled with the {\verb -fPIC }
flag in \ac{GCC}. This flag basically tells the compiler that the
machine code must be able to execute anywhere in memory, also known as position
independent. In runtime one extra \ac{CPU} register will be used for this. This
is needed because a Python C module we will need to be compiled as a shared
library.

Since Tahoe-\ac{LAFS} is using \ac{SHA}-256 internally, we only test \ac{SHA}-3
functions with 256-bit output to avoid problems that could be caused by longer 
hash values in Tahoe-\ac{LAFS}.

@@

We chose the fastest implementation of each candidate that conforms to the
following criteria:
\paragraph{Criterion 1} The implementation must have an \ac{API} defined in C.
\paragraph{Criterion 2} The implementation must include a working {\verb update() } function.
\paragraph{Criterion 3} The implementation must not use code that can not be made
    position independent by \ac{GCC}.
\paragraph{Criterion 4} The implementation should conform to the \acp{KAT} specified in the
    \ac{NIST} submission package, or later updates by the author.

\vspace{12pt}
Based on these criteria, we choose the fastest possible implementation based on
our benchmark in \ac{SUPERCOP} \cite{s_tahoe_supercop}. The relative speed of
each implementation, in relation to other implementation for the same and other
candidates can be found at eBASH\cite{s_tahoe_supercop}.

@@

The chosen implementations are shown in Table \ref{tbl:sha3:implementations}.
Their compiler flags used, which are extracted from the \ac{SUPERCOP} results,
can be seen in Table \ref{tbl:sha3:compilerflags}. Compiler flags are described
in the GCC manual\footnote{GCC Manual \url{http://gcc.gnu.org/onlinedocs/}},
and the flags used for every implementation which might affect performance, are:

@@

\paragraph{JH} seems to be broken in every implementation with regard to
Criterion 2. For both the optimized versions found in \ac{SUPERCOP}, and the
reference implementations in the \ac{NIST} submission package,
{\verb Hash("foofoo") } will not yield the same result as two consecutive calls
to {\verb Update("foo") }. However, the implementation in sphlib does fulfill
this requirement. We have contacted the author of sphlib, Thomas Pornin, which confirms
this problem with the official JH candidate, and that the author has been made
aware of the problem, but has not released any updated version yet
\cite{s_pornin}.

@@

Our original goal was to make SHA3lib include functionality to support all
output lengths, and not only 256-bit. This was based on our observation that the
official \ac{NIST} submission packages include ``all-in-one'' implementations
that support this. Later we observed that this is not the case for all
implementations in \ac{SUPERCOP}. Together with the fact that Tahoe-\ac{LAFS}
uses 256-bit output, in the end only support for 256-bit output in
SHA3lib was implemented. The design we have used is shown in Figure
\ref{fig:python:inheritance}, and does follow the initial idea that SHA3lib
should support multiple output lengths.

@@

Basically the class \textbf{echo} resides in Cython and in C, and is responsible
for bringing the functionality of the \ac{SHA}-3 candidate implementation to Python. By compiling
\textbf{echo} it will be made available for use in Python.  The class
\textbf{echo256} is a simple Python class which inherits from \textbf{echo}. The
only action this class actually performs, is to set the output size to 256 bit. If
the underlying C-functions would have supported multiple output sizes, the same
could have been done to incorporate those.

@@

We then create a wrapper-class that mimics hashlib, this is shown in Listing
\ref{lst:cython_impl}. Functions declared with {\verb def } are Python
functions, {\verb cdef } are Cython-only functions, while {\verb cpdef } are
functions that can be accessed from both languages. While this is just the
implementation for the Echo implementation, the almost exact same pattern is used for
all of the other candidates.

@@

\subsection{Unit tests}
We Unit Test each new candidate implementation that is included in SHA3lib, both
to verify our own work and to verify that the implementations from \ac{SUPERCOP}
actually are correct.

@@

All hashing operations requested by the Tahoe system is routed through a
couple of classes and functions, and the connection to the underlying hash
function library is made in only one line. This is displayed in Listing
\ref{lst:hashutil}.

@@

\section{Automatic testing and distribution} We fully automate the testing
procedure. This is achieved by the use of software revision control systems,
which distributes both the source code of Tahoe-\ac{LAFS}, SHA3lib and
shell-scripts for installation and configuration of both. Configuration is
mainly done by the use of regular expressions.The outline of this procedure is:

@@

BLAKE, \ac{BMW}, and Luffa outperform \ac{SHA}-256 on cycles per
byte for all tests. For larger input sizes, Simd and Shabal also do the
calculations quicker than \ac{SHA}-256.
